Probability of causal contact between interstellar civilizations through MonteCarlo simulations

### 2019-08-12 manuscript.tex
manuscript

\subsection{Reciprocal communication}
%{{{

@@

   \includegraphics[width=0.33\textwidth]{prob1_10k.png}%
   \includegraphics[width=0.33\textwidth]{prob1_40k.png}%
   \includegraphics[width=0.33\textwidth]{prob1_80k.png}

   \caption{Fraction of the CETIs that have made at least one contact  
   as a funtion of the elapsed time since the awakening, given that
   they make at least one contact on their lifetime.}
   \label{F_}
\end{figure*}

\begin{figure*}
   \centering
   \caption{}
   \label{F_}
\end{figure*}

>>>>

In the Fig.~\ref{F_waiting} we show the fraction of the CETIs that
have made at least one contact  as a funtion of the elapsed time since
the awakening, given that they make at least one contact on their
lifetime.
%
From a frequentist approach, the normalizaed cumulative counts are
related to the estimation of the probability of observing a given time
with no success.
%             
XX panels show the histograms of the waiting times for the first
contact, for all the CETIs that make at least one contact along their
lifetime.
%
We show separately the histograms for several values of $\tau_a$ and a
fixed value of $(\tau_s, D_{max})$, and for several values of $\tau_s$ and a
fixed value of $(\tau_a, D_{max})$.
%
For different values of $\tau_a$, the shape of the distribution is
similar, so that a normalization ... but not in the case of different values of $\tau_s$.

@@

   \caption{Fraction of the CETIs that have made at least one contact  
   as a funtion of the elapsed time since the awakening, given that
   they make at least one contact on their lifetime.
   %
   From a frequentist approach, this fraction is the estimation of the
   probability

   }
   \label{F_waiting}
\end{figure*}

\begin{figure*}
   \centering
   \includegraphics[width=0.33\textwidth]{prob1_10k.png}%
   \includegraphics[width=0.33\textwidth]{prob1_40k.png}%
   \includegraphics[width=0.33\textwidth]{prob1_80k.png}

   \caption{F_}
   \label{F_waiting}
\end{figure*}
